Analysis of the 2005--\myrevision{2016} Earthquake Sequence in Northern Iran Using the Visibility Graph Method

### 2017-06-21 methodology.tex
updates on modifications of the revised version for paag
update (cont.) to paag revision

\begin{figure*}[t]
	\centering
	\includegraphics[width=0.8\textwidth]{figures/pdf/figure-01} 
	\caption{Illustration of the visibility graph method, as applied to a subset of events in a window of the magnitude-time series of the north Iranian seismic region of Kopeh Dagh. The events are identified by vertical thick lines (or sticks) on the horizontal time axis with size equal to the magnitude as indicated by the labels at the bottom of each stick. These sticks are considered to be the obstacles in the time-magnitude space where the graph resides. The visibility graph is composed by the nodes, represented with circles at the tip of each event stick, and the edges or links connecting them. The values inside each node correspond to the connectivity degree, $k$. This value indicates the number straight lines that can be draw between two (mutually visible) nodes without intersecting any obstacle (event stick). The values and time ranges shown at the top correspond to the time difference between events visible by the last event. These times are given in minutes and correspond to individual $T_c$ values. The mean $<$$T_c^e$$>$ value associated with this event is also shown at the top right. The mean value of all $<$$T_c^e$$>$ for the events in the graph is the window mean interval connectivity time, $<$$T_c^e$$>$. The color version of this figure is available only in the electronic edition.}
	\label{fig:vg}
\end{figure*}

@@

>>>>

\begin{figure*}[t]
	\centering
	\includegraphics[width=0.8\textwidth]{figures/pdf/figure-01} 
	\caption{Illustration of the visibility graph method, as applied to a subset of events in a window of the magnitude-time series of the north Iranian seismic region of Kopeh Dagh. The events are identified by vertical thick lines (or sticks) on the horizontal time axis with size equal to the magnitude as indicated by the labels at the bottom of each stick. These sticks are considered to be the obstacles in the time-magnitude space where the graph resides. The visibility graph is composed by the nodes, represented with circles at the tip of each event stick, and the edges or links connecting them. The values inside each node correspond to the connectivity degree, $k$. This value indicates the number straight lines that can be draw between two (mutually visible) nodes without intersecting any obstacle (event stick). The values and time ranges shown at the top correspond to the time difference between events visible by the last event. These times are given in minutes and correspond to individual $T_c$ values. The mean $<$$T_c^e$$>$ value associated with this event is also shown at the top right. The mean value of all $<$$T_c^e$$>$ for the events in the graph is the window mean interval connectivity time, $<$$T_c^e$$>$.}
	\label{fig:vg}
\end{figure*}

@@

% OLD MATERIAL
% -----------------------------------------------------------------

### 2017-06-21 results.tex
update (cont.) to paag revision

\begin{figure*}[t]
	\centering
	\includegraphics[width=\textwidth]{figures/pdf/figure-06} 
	\caption{Scattered distribution of events in the magnitude-connectivity degree plane and linear regressions obtained for the $k$-$M$ relationships for the three seismic regions in northern Iran. The value next to each of regression line corresponds to the slope of the line, which is referred here as the $k$-$M$ slope. The color version of this figure is available only in the electronic edition.}
	\label{fig:km}
\end{figure*}

@@

\begin{figure*}[t]
	\centering
	\includegraphics[width=\textwidth]{figures/pdf/figure-07} 
	\caption{\myrevision{Correlation between $k$-$M$ slope ($m$) and the $b$ value as drawn from the results of the present study for the region of northern Iranian using the complete (a) and declustered (b) catalogs, along with other previous studies including analysis of the Mexican subduction zone \citep{Telesca2013}, the Pannonian seismic zone \citep{Telesca2014}, southern California \citep{Azizzadeh_2017_SSA}, and results from two experiments \citep{Telesca2014-pone}. The lines represent linear regressions obtained to fit the different data points, considering different combinations. The values of the correlation coefficient, $R$, are indicated for each regression line. The color version of this figure is available only in the electronic edition.}}
	\label{fig:regression}
\end{figure*}

@@

\begin{figure*}%[t]
	\centering
	\includegraphics[width=0.9\textwidth]{figures/pdf/figure-08-rev.pdf} 
	\caption{\textbf{(a)} Correlation between $k$-$M$ slope and $b$-values for 200 random sequences extracted from the \myrevision{whole} catalogs of the three northern Iranian seismic regions considered in this study (scattered symbols), including the mean values (empty symbols with thick border) and the data points obtained from the analysis of the complete catalog (solid symbols), along with the linear regressions of each sample as indicated in the legend. \textbf{(b)} Mean, $\pm1$ standard deviation, and coefficient of variation (in percent) for the $k$-$M$ slope values of the three seismic zones in northern Iran. \textbf{(c)} Same as part (b), but corresponding to the $b$-value. The color version of this figure is available only in the electronic edition.}
	\label{fig:random}
\end{figure*}

>>>>

\begin{figure*}[t]
	\centering
	\includegraphics[width=\textwidth]{figures/pdf/figure-06} 
	\caption{Scattered distribution of events in the magnitude-connectivity degree plane and linear regressions obtained for the $k$-$M$ relationships for the three seismic regions in northern Iran. The value next to each of regression line corresponds to the slope of the line, which is referred here as the $k$-$M$ slope.}
	\label{fig:km}
\end{figure*}

@@

\begin{figure*}[t]
	\centering
	\includegraphics[width=\textwidth]{figures/pdf/figure-07} 
	\caption{\myrevision{Correlation between $k$-$M$ slope ($m$) and the $b$ value as drawn from the results of the present study for the region of northern Iranian using the complete (a) and declustered (b) catalogs, along with other previous studies including analysis of the Mexican subduction zone \citep{Telesca2013}, the Pannonian seismic zone \citep{Telesca2014}, southern California \citep{Azizzadeh_2017_SSA}, and results from two experiments \citep{Telesca2014-pone}. The lines represent linear regressions obtained to fit the different data points, considering different combinations. The values of the correlation coefficient, $R$, are indicated for each regression line.}}
	\label{fig:regression}
\end{figure*}

@@

\begin{figure*}%[t]
	\centering
	\includegraphics[width=0.9\textwidth]{figures/pdf/figure-08} 
	\caption{\myrevision{Correlation between the $k$-$M$ slope ($m$) and $b$ values for 200 random sequences extracted from the complete (a) and declustered (d) catalogs of the three northern Iranian seismic regions considered in this study (scattered symbols), including the mean values (empty symbols with thick border) and the data points obtained from the regional analyses (solid symbols), along with the linear regressions of each sample as indicated in the legend; and mean $\pm1$ standard deviation bar plots for $m$ (b,e) and $b$ (c,f) for the complete and declustered catalogs, respectively. In the latter, the values in the parentheses corresponds to the coefficients of variation.}}
	\label{fig:random}
\end{figure*}

### 2017-06-21 seismicity.tex
update (cont.) to paag revision

\begin{figure*}[t]
	\centering
	\includegraphics[width=\textwidth]{figures/pdf/figure-02} 
	\caption{Region of interest, highlighting the seismic zones that are the focus of this study: Azerbaijan, Alborz, and Kopeh Dagh. The top-right location-map shows Iran and the selected area with respect to neighboring countries. The solid dark lines show the boundaries of the additional Zagros and Central-East seismic zones. This zonation follows the division proposed by \citet{Mirzaei1998} and later modified by \citet{Karimiparidari2013}. The background shows fault lines and the shaded relief. The color version of this figure is available only in the electronic edition.}
	\label{fig:study_region}
\end{figure*}

@@

\begin{figure*}[t]
	\centering
	\includegraphics[width=\textwidth]{figures/pdf/figure-03} 
	\caption{\myrevision{Instrumental seismicity of northern Iran for the 2005--2016 period, considering only the events in the seismic zones of interest, namely Azerbaila, Alborz, and Kopeh Dagh, for the whole (a) and complete (b) catalogs.} The size of symbols are proportional to the magnitude of the events, as indicated by the artificial scale shown on the right. The background shows fault lines and the shaded relief. The color version of this figure is available only in the electronic edition.}
	\label{fig:seismicity}
\end{figure*}

@@

\myrevision{
\begin{table*}
	\caption{Total number of earthquakes \myrevision{for the whole, complete, and declustered catalogs}, and seismic parameters $M_c$ and $b$ \myrevision{(including standard deviation) for the complete catalogs} of the three seismic zones of northern Iran.}
	\centering\small
	\myrevision{
	\begin{tabular}{lcccccc}
		\hline
		Region       & \multicolumn{3}{c}{Number of Events in Catalog} & $M_c$ & \multicolumn{2}{c}{$b$-value} \\
		\cline{2-4} 
		             & Whole & Complete & Declustered &     & Complete             & Declustered \\
		\hline
		Azerbaijan   & 1047  &  202     &     ?       & 3.5 & 0.85491 $\pm$ 0.0506 & ? \\
		Alborz       & 1898  &  575     &     ?       & 3.0 & 0.81578 $\pm$ 0.0279 & ? \\
		Kopeh Dagh   &  640  &  117     &     ?       & 3.5 & 0.78297 $\pm$ 0.0494 & ? \\
		\hline
	\end{tabular}
	}
	\label{tab:seismicity}
\end{table*}
}

\begin{figure*}%[t]
	\centering
	\includegraphics[width=\textwidth]{figures/pdf/figure-05-rev} 
	\caption{Time-magnitude sequences for the northern Iran seismic zones of Azerbaijan, Alborz and Kopeh Dagh, during the period between 1 January 2005 and 31 December \myrevision{2016}. The event occurrences are represented by vertical bars or sticks of length equal to the $M_w$ magnitude of each earthquake. These sequences correspond to the \myrevision{whole} catalog but in each case we consider only events with $M_w \geq M_c$. As shown in Fig.~\ref{fig:vg}, the dots at the top of each stick represent the nodes of the visibility graphs. The edges or links are omitted for visual convenience. Highlighted in the figure are the largest events in each sub-catalog, namely the 2012 $M_w$ 6.4 East Azerbaijan, 2010 $M_w$ 5.8 Damghan, and 2012 $M_w$ 5.4 Neyshabur earthquakes. The color version of this figure is available only in the electronic edition.}
	\label{fig:mag-time}
\end{figure*}

>>>>

\begin{figure*}[t]
	\centering
	\includegraphics[width=\textwidth]{figures/pdf/figure-02} 
	\caption{Region of interest, highlighting the seismic zones that are the focus of this study: Azerbaijan, Alborz, and Kopeh Dagh. The top-right location-map shows Iran and the selected area with respect to neighboring countries. The solid dark lines show the boundaries of the additional Zagros and Central-East seismic zones. This zonation follows the division proposed by \citet{Mirzaei1998} and later modified by \citet{Karimiparidari2013}. The background shows fault lines and the shaded relief.}
	\label{fig:study_region}
\end{figure*}

@@

\begin{figure*}[t]
	\centering
	\includegraphics[width=\textwidth]{figures/pdf/figure-03} 
	\caption{\myrevision{Instrumental seismicity of northern Iran for the 2005--2016 period, considering only the events in the seismic zones of interest, namely Azerbaila, Alborz, and Kopeh Dagh, for the whole (a) and complete (b) catalogs.} The size of symbols are proportional to the magnitude of the events, as indicated by the artificial scale shown on the right. The background shows fault lines and the shaded relief.}
	\label{fig:seismicity}
\end{figure*}

@@

\myrevision{
\begin{table*}
	\caption{Total number of earthquakes \myrevision{for the whole, complete, and declustered catalogs}, and seismic parameters $M_c$ and $b$ \myrevision{(including standard deviation) for the complete catalogs} of the three seismic zones of northern Iran.}
	\centering\small
	\myrevision{
	\begin{tabular}{lcccccc}
		\hline
		Region       & \multicolumn{3}{c}{Number of Events in Catalog} & $M_c$ & \multicolumn{2}{c}{$b$-value} \\
		\cline{2-4}\cline{6-7} 
		             & Whole & Complete & Declustered &     & Complete             & Declustered \\
		\hline
		Azerbaijan   & 1047  &  202     &     ?       & 3.5 & 0.85491 $\pm$ 0.0506 & ? \\
		Alborz       & 1898  &  575     &     ?       & 3.0 & 0.81578 $\pm$ 0.0279 & ? \\
		Kopeh Dagh   &  640  &  117     &     ?       & 3.5 & 0.78297 $\pm$ 0.0494 & ? \\
		\hline
	\end{tabular}
	}
	\label{tab:seismicity}
\end{table*}
}

\begin{figure*}%[t]
	\centering
	\includegraphics[width=\textwidth]{figures/pdf/figure-05} 
	\caption{Time-magnitude sequences for the northern Iran seismic zones of Azerbaijan, Alborz and Kopeh Dagh, during the period between 1 January 2005 and 31 December \myrevision{2016}. The event occurrences are represented by vertical bars or sticks of length equal to the $M_w$ magnitude of each earthquake. These sequences correspond to the \myrevision{whole} catalog but in each case we consider only events with $M_w \geq M_c$. As shown in Fig.~\ref{fig:vg}, the dots at the top of each stick represent the nodes of the visibility graphs. The edges or links are omitted for visual convenience. Highlighted in the figure are the largest events in each sub-catalog, namely the 2012 $M_w$ 6.4 East Azerbaijan, 2010 $M_w$ 5.8 Damghan, and 2012 $M_w$ 5.4 Neyshabur earthquakes.}
	\label{fig:mag-time}
\end{figure*}
